Visualizing probability distributions across bivariate nonlinear temporal granularities

### 2020-02-17 main.Rmd
Query on Section 3

In general, any circular granularity relating two linear granularity, none of which are bottom granularity can be expressed as $C_{(G, H)}(z) = L(\lfloor z/P(B,G) \rfloor\mod P(G,H))$, where linear granularity $H$ is periodic with respect to linear granularity $G$ with regular mapping such that the number of granules of $G$ in each granule of $H$ is $P(G,H)$. Table \ref{tab:definitions} shows representation of circular granularities $C_i$ relating two linear granularities with $P_i$ being the number of granules of the finer granularity in each granule of the coarser granularity and $L_i$ is the associated label mapping. It is possible that none of the two linear granularities are bottom granularities. But the representation of the resultant circular granularity will be a function of the index set. The bottom granularity is assumed to be minutes.

>>>>

In general, any circular granularity relating two linear granularity, none of which are bottom granularity\todo{Why not?} can be expressed as $C_{(G, H)}(z) = L(\lfloor z/P(B,G) \rfloor\mod P(G,H))$, where linear granularity $H$ is periodic with respect to linear granularity $G$ with regular mapping such that the number of granules of $G$ in each granule of $H$ is $P(G,H)$. Table \ref{tab:definitions} shows representation of circular granularities $C_i$ relating two linear granularities with $P_i$ being the number of granules of the finer granularity in each granule of the coarser granularity and $L_i$ is the associated label mapping. It is possible that none of the two linear granularities are bottom granularities. But the representation of the resultant circular granularity will be a function of the index set. The bottom granularity is assumed to be minutes.
